\subsection{Artificial Intelligence (AI)}

Our AI offers three path finding algorithms:
\begin{itemize}
  \item Greedy Search;
  \item Uniform Cost Search;
  \item A* Search.
\end{itemize}

The first one is incomplete and not optimal because of the local search which looks only one step ahead (visiting
only the neighbors). The last two algorithm are both complete and optimal under certain assumptions. They have been defined
to guarantee our agents to always find the best possible path with the minimum number of visited nodes in the search graph.

To guarantee completeness we need to assume that each graph is a strongly
connected component. Basically, it means that there are no isolated
components. Thus, the agent knows there will always be at least a path between
the source and the destination of its plan. % its or her

Furthermore, our AI considers not grid based maps: which means some common
heuristics are not applicabile a priori (e.g. Manhattan distance, euclidean
distance). Also, since grid-based maps are a subset of all possible maps, we
can say that our AI is independent on the map topology.

To solve the path finding problem we reason about the specific domain and its
abstractions in terms of infrastructure building blocks and travelers. We
found an admissibile and consistent heuristic for A* and in general other
informed algorithms. To concretely guarantee the assumptions hold for all the
graph configurations we apply the Tarjan algorithm.

Tarjan automatically validates our graphs at build time by ensuring that there
is only one strong connected component for each graph, otherwise it reports
an error and shows the isolated component.
Finally, the AI is agent-independent, which means we can use it to calculate
the path of different kinds of agents: bicycles which move on bicycle lanes,
pedestrians who move on sidewalks and motor vehicles which move on roads.
